\documentclass[a4paper,12pt,titlepage]{report}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{fullpage}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{tikz3d}
\usepackage{pgfplots}
\usepackage{ifthen}
\usepackage[outline]{contour}
\usepackage{color}

% Grab the required TikZ libraries
\usetikzlibrary{ hexagon
               , calc
               , backgrounds
               , positioning
               , decorations.pathreplacing
               , decorations.markings
               , arrows
               , positioning
               , automata
               , shadows
               , fit
               , shapes
               , arrows
               , patterns
               }

% Cache TikZ figures
\usetikzlibrary{external}
\tikzexternalize[prefix=tikzcache/]

% Remove borders etc. from links added by hyperref
\hypersetup{
	colorlinks=false,
	pdfborder={0 0 0},
}

% When adding a border around some text, this is how thick it should be.
\contourlength{1.5pt}

\title{An Improved Interconnection Network for the Next Generation of Brain
Simulators}
\author{Jonathan Heathcote}
\date{The University of Manchester}

% Number subsubsections
\setcounter{secnumdepth}{3}

\begin{document}
	
	\maketitle
	
	\begin{abstract}
		
		Many attempts to understand the vast complexity of the human brain centre on
		simulating models of its behaviour. Conventional supercomputers have failed
		to provide the necessary power to execute large-scale models of the brain's
		function leading to the development of special purpose `neuromorphic'
		hardware such as SpiNNaker.
		
		This project aims to advance the way in which high-speed serial (HSS)
		technology is used in neural simulation systems. SpiNNaker, like other
		neural simulators, is beginning to exploit HSS links in parts of its
		interconnection network and future versions may move entirely to HSS-based
		networks.
		
		Preliminary work has tackled practical issues involved in the wiring of
		large machines using HSS interconnect and developed a simple extension which
		can deliver lower latency and higher throughput with little additional
		wiring cost. Additionally, accurate models of SpiNNaker's interconnect were
		built which will be used to verify these extensions prior to trail
		implementation in SpiNNaker.
		
		Work is proposed to develop power management strategies for HSS links which
		are appropriate for neural simulations. Such simulations may have hard
		latency requirements which existing HSS power management schemes don't meet.
		These changes will be validated within existing SpiNNaker hardware.
		
	\end{abstract}
	
	\tableofcontents
	\listoffigures
	%\listoftables
	
	\input{introduction}
	\input{background}
	\input{preliminary-work}
	\input{research-plan}
	\input{conclusion}
	
	% Number bib entries by order of appearance
	\bibliographystyle{unsrt}
	\bibliography{report}
	
\end{document}
